\chapter{ERIKA3 user guide }
\hypertarget{index}{}\label{index}\index{ERIKA3 user guide@{ERIKA3 user guide}}
ERIKA3 is an open-\/source AUTOSAR OS implementation, \href{http://www.erika-enterprise.com}{\texttt{available for download}} under \href{http://www.erika-enterprise.com/index.php/erika3/licensing.html}{\texttt{various licensing terms, including a GPLv2 license}}.

This document contains the reference manual for ERIKA3, which is divided in the following Chapters\+:

The document is divided in the following Chapters\+:

\tabulinesep=1mm
\begin{longtabu}spread 0pt [c]{*{2}{|X[-1]}|}
\hline
\PBS\centering \cellcolor{\tableheadbgcolor}\textbf{ Chapter  }&\PBS\centering \cellcolor{\tableheadbgcolor}\textbf{ Description  }\\\cline{1-2}
\endfirsthead
\hline
\endfoot
\hline
\PBS\centering \cellcolor{\tableheadbgcolor}\textbf{ Chapter  }&\PBS\centering \cellcolor{\tableheadbgcolor}\textbf{ Description  }\\\cline{1-2}
\endhead
\doxylink{intro}{Introduction to ERIKA3 and RT-\/\+Druid}  &A first introduction to ERIKA3.  \\\cline{1-2}
\doxylink{implemented-standards}{Implemented Standards}  &The OS API standards implemented in ERIKA3.  \\\cline{1-2}
\doxylink{scheduler}{ERIKA3 and real-\/time scheduling}  &The scheduling algorithms implemented in ERIKA3.  \\\cline{1-2}
\doxylink{system-init}{System and application initialization}  &System initialization details.  \\\cline{1-2}
\doxylink{task-types}{Basic and Extended tasks}  &The task types in ERIKA3.  \\\cline{1-2}
\doxylink{stack-sharing}{Stack sharing in ERIKA3}  &Stack Sharing in ERIKA3.  \\\cline{1-2}
\doxylink{irq}{Interruput handlers}  &IRQ handling in ERIKA3.  \\\cline{1-2}
\doxylink{resources}{Mutual Exclusion and Shared resources}  &Shared resource handling in ERIKA3  \\\cline{1-2}
\doxylink{multicore}{Multicore support}  &Multicore support in ERIKA3  \\\cline{1-2}
\doxylink{apireference}{ERIKA3 API reference}  &ERIKA3 API reference.  \\\cline{1-2}
\doxylink{orti}{ORTI support in ERIKA3}  &ORTI support in ERIKA3.  \\\cline{1-2}
\end{longtabu}


Additional information is finally available as well in the \href{http://www.erika-enterprise.com/wiki}{\texttt{ERIKA3 wiki}}, and in the \href{http://www.erika-enterprise.com/forum}{\texttt{ERIKA3 Forum}}. \input{intro}
\input{implemented-standards}
\input{scheduler}
\input{system-init}
\input{task-types}
\input{stack-sharing}
\input{irq}
\input{resources}
\input{multicore}
\input{apireference}
\input{orti}
